The Dark \LaTeX{} \\ \large An Example of the dndbook Class

### 2020-01-17 example.tex
Fixed up the background "paper image" option so that it defaults to the standard one without having to be explicitly defined in the document

\documentclass[letterpaper,twocolumn,openany]{dndbook}

@@

% Set the default background paper-like image. This options allows it to be overridden.
\paperimage{img/paper}

@@

\paragraph{Paragraph}
The paragraph format is seldom used in the core books, but is available if you prefer the other style.

@@

\section{Map Regions}
The map region functions |\area| and |\subarea| provide automatic numbering of areas.

@@

\begin{lstlisting}
\begin{DndTable}[cX][PhbLightCyan]
  \textbf{d8} & \textbf{Item} \\
  1           & Small wooden button \\
  2           & Red feather \\
  3           & Human tooth \\
  4           & Vial of green liquid \\
  6           & Tasty biscuit \\
  7           & Broken axe handle \\
  8           & Tarnished silver locket \\
\end{DndTable}
\end{lstlisting}

@@

\begin{DndSidebar}{This Sidebar Is Also Mauve}
  The sidebar is also using the new theme color.
\end{DndSidebar}

\endgroup

>>>>

\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode]{dndbook}

@@

% Uncomment to allow the default background paper image to be overridden.
%\SetPaperImage{img/paper}

@@

\paragraph{Paragraph}
The paragraph format is seldom used in the core books, but is available if you prefer it to the ``normal'' style.

@@

\section{Map Regions}
The map region functions |\DndArea| and |\DndSubArea| provide automatic numbering of areas.

@@

\begin{lstlisting}
\begin{DndTable}[color=PhbLightCyan]{cX}
  \textbf{d8} & \textbf{Item} \\
  1 & Small wooden button \\
  2 & Red feather \\
  3 & Human tooth \\
  4 & Vial of green liquid \\
  6 & Tasty biscuit \\
  7 & Broken axe handle \\
  8 & Tarnished silver locket \\
\end{DndTable}
\end{lstlisting}

@@

\begin{DndSidebar}{This Sidebar Is Also Mauve}
  The sidebar is also using the new theme color.
\end{DndSidebar}
\endgroup
